Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-01-16 paper/ms.tex
my version of the extended system of equations

@@

\citet{Ambikasaran:2015} demonstrated two key facts that allow us to use this
extended matrix formalism in practice.
First, even if the covariance function is a mixture of exponentials, the
extended matrix will still be banded with bandwidth \dfmtodo{check}.
Second, \citet{Ambikasaran:2015} proved that the determinant of
$K_\mathrm{ext}$ is equal to the determinant of $K$ up to a sign.

>>>>

\citet{Ambikasaran:2015} demonstrated two key facts that allow us to use this
extended matrix formalism in practice.
First, even if the covariance function is a mixture of exponentials, the
extended matrix will still be banded with a bandwidth that scales linearly
with the number of components $J$.
Second, \citet{Ambikasaran:2015} proved that the determinant of
$K_\mathrm{ext}$ is equal to the determinant of $K$ up to a sign.
This means that we can use this extended matrix formalism to compute the
marginalized likelihood in $\mathcal{O}(N\,J^2)$ operations.

@@

In this section, we generalize the method from the previous section to the
covariance function given by \eq{celerite-kernel-complex}.
This derivation follows \citet{Ambikasaran:2015} but it includes explicit
treatment of complex parameters.

\begin{eqnarray}
\phi_{n,j} &=& e^{-c_j\,\tau_{n+1,n}}\,\cos\left(d_j\,\tau_{n+1,n}\right)\\
\psi_{n,j} &=& -e^{-c_j\,\tau_{n+1,n}}\,\sin\left(d_j\,\tau_{n+1,n}\right)\\
g_{n,j} &=& \phi_{n,j}\,g_{n-1,j} + \phi_{n,j}\,x_n + \psi_{n,j}\,h_{n-1,j}\\
h_{n,j} &=& \phi_{n,j}\,g_{n-1,j} - \psi_{n,j}\,x_n - \psi_{n,j}\,h_{n-1,j}\\
u_{n,j} &=& \phi_{n+1,j}\,u_{n+1,j} + \frac{a_j}{2}\,x_n + \psi_{n+1,j}\,v_{n+1,j}\\
v_{n,j} &=& \phi_{n+1,j}\,u_{n+1,j} - \frac{b_j}{2}\,x_n - \psi_{n+1,j}\,v_{n+1,j}
\end{eqnarray}

\begin{eqnarray}
\sum_{j=1}^J \left[\frac{a_j}{2}\,g_{n,j}+\frac{b_j}{2}\,h_{n,j}\right]
+ \left[{\sigma_n}^2+\sum_{j=1}^J a_j\right]
+ \sum_{j=1}^J \left[\phi_{n,j}\,u_{n,j}+\psi_{n,j}\,v_{n,j}\right]
    &=& y_n
\end{eqnarray}
